title: "Course Project:Shiny Application and Reproducible Pitch"

author: "Michelle Tan"

date: "1/20/2018"

output: ioslides_presentation

##
First Slide
Diamond Analysis Report
Diamond Data Analysis Report enabled developing data products using shiny apps being embeded within RMarkDown.

Using PageUp and PageDown keys all the slides can be traversed.

For more details on authoring R presentations please visit <http://rpubs.com/Michelletan78/350843>.
This presentation contains documentation for the Diamond price prediction application. The application can be found [**here**] 

This application it is building linear regression model using `diamonds` data set and is predicting the price of a diamond depending of its properties.The application allows the user to select:

##Second slide
Application Overview
- Bullet 1
Diamonds Properties can be analysed using several Parameters.
- Bullet 2
Carat,Price,sample size,color Depth are some of the common parameters.
- Bullet 3
This Report enables to pick the right parameters for the best Diamond selection.

##
Slide With Code
The data used for this application is diamonds data set, which is part of ggplot2 package. Containing information about 53940 diamonds with 10 variables.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r diamonds, echo = FALSE}
summary("diamonds")
```

## Slide with Plot

```{r }
library("ggplot2")
head(diamonds)
```

